Revisiting the hydrodynamic modulation of short surface waves by longer waves

### 2025-03-13 paper.tex
Shorten abstract to fit 250 word limit

\begin{abstract}
Hydrodynamic modulation of short ocean surface waves by longer ambient waves is
a well-known ocean surface process that affects remote sensing, the
interpretation of \textit{in situ} wave measurements, and numerical wave
forecasting.
In this paper, we revisit the wave crest and action conservation laws and derive
higher-order steady solutions for the change of short-wave wavenumber, action,
and gravitational acceleration due to the presence of longer waves.
We validate the analytical solutions with numerical simulations of the full wave
crest and action conservation equations.
The nonlinear analytical solutions of short-wave wavenumber, amplitude, and
steepness modulation significantly deviate from the linear analytical solutions
of \citet{longuet1960changes}, and are similar to the nonlinear numerical
solutions by \citet{longuet1987propagation} and \citet{zhang1990evolution}.
The short-wave steepness modulation is attributed to be 5/8 due to the
wavenumber, 1/4 due to the wave action, and 1/8 due to the effective gravity.
Examining the homogeneity and stationarity requirements for the conservation of
wave action reveals that stationarity is a stronger requirement and is
generally not satisfied for very steep long waves.
We further examine the results of \citet{peureux2021unsteady} who found through
numerical simulations that the short-wave modulation grows unsteadily with
each long-wave passage.
We show that this unsteady growth only occurs for homogeneous initial
conditions as a special case and does not generally occur, for example, in more
realistic long-wave groups.
The proposed steady solutions are a good approximation of the nonlinear
crest-action conservation solutions in long-wave steepness $\lesssim 0.2$.
Except for a subset of initial conditions, the solutions to the non-linearised
crest-action conservation equations are mostly steady in the reference frame of
the long waves.
\end{abstract}

>>>>

\begin{abstract}
Hydrodynamic modulation of short ocean surface waves by longer ambient waves
significantly influences remote sensing, interpretation of \textit{in situ} wave
measurements, and numerical wave forecasting.
This paper revisits the wave crest and action conservation laws and derives
steady, nonlinear, analytical solutions for the change of short-wave wavenumber,
action, and gravitational acceleration due to the presence of longer waves.
We validate the analytical solutions with numerical simulations of the full 
conservation equations.
The nonlinear analytical solutions of short-wave wavenumber, amplitude, and
steepness modulation significantly deviate from the linear analytical solutions
of \citet{longuet1960changes}, and are similar to the nonlinear numerical
solutions by \citet{longuet1987propagation} and \citet{zhang1990evolution}.
The short-wave steepness modulation is attributed 5/8 to
wavenumber, 1/4 due to wave action, and 1/8 due to effective gravity.
Examining the homogeneity and stationarity requirements for the conservation of
wave action reveals that stationarity is a stronger requirement and is
generally not satisfied for very steep long waves.
We examine the results of \citet{peureux2021unsteady} who found through
numerical simulations that the short-wave modulation grows unsteadily with
each long-wave passage.
We show that this unsteady growth only occurs for homogeneous initial
conditions as a special case and not generally.
The proposed steady solutions are a good approximation of the nonlinear
crest-action conservation solutions in long-wave steepness $\lesssim 0.2$.
Except for a subset of initial conditions, the solutions to the non-linearised
crest-action conservation equations are mostly steady in the reference frame of
the long waves.
\end{abstract}
